Cosmological constraints from the redshift dependence of the volume effect using the galaxy 2-point correlation function across the line-of-sight

### 2017-04-01 draft/draft2.1_cris.tex
updates

\title{Cosmological constraints from the redshift dependence of the volume effect: galaxy angular 2-point correlation function}

%\author{Xiao-Dong~Li\altaffilmark{1}, Changbom~Park\altaffilmark{1}, J.~E.~Forero-Romero\altaffilmark{2} and Juhan Kim%\altaffilmark{3}}
%\affil{\altaffilmark{1}School of Physics, Korea Institute for Advanced Study, Heogiro 85, Seoul 130-722, Korea }
%\affil{\altaffilmark{2}Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, %Colombia}
%\affil{\altaffilmark{3}Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-%gu, Seoul 130-722, Korea }
%\affil{\it (xiaodongli@kias.re.kr, cbp@kias.re.kr, je.forero@uniandes.edu.co, kjhan@kias.re.kr)}

@@

\author{Xiao-Dong Li, Changbom Park, }
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\author{Cristiano G. Sabiu\altaffilmark{1}, Hyunbae Park, }
\affil{Korea Astronomy and Space Science Institute, Daejeon 305-348, Korea}
%\author{David H. Weinberg,}
%\affil{Department of Astronomy and CCAPP, The Ohio State University, 140 West 18th Avenue, Columbus, OH 43210, USA}
%\author{Donald P. Schneider,}
%\affil{Department of Astronomy and Astrophysics, The Pennsylvania State University, 
%University Park, PA 16802 }
%\affil{Institute for Gravitation and the Cosmos, The Pennsylvania State University, 
%University Park, PA 16802 }
\author{Cheng Cheng, }
\affil{Kavli Institute for Theoretical Physics China, Institute of Theoretical Physics, Chinese Academy of Sciences, Zhong Guan Cun Street 55\#, Beijing, 100190, P.R. China}
\affil{University of Chinese Academy of Sciences, P.R. China}
\author{Juhan Kim,}
\affil{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\and
\author{Sungwook E. Hong}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}

@@

\begin{abstract}
{\bf Let us use 1) angular CF across the line-of-sight 2) $\xi_{\bot}$ rather than $\omega_{r_{\bot}}$}
We propose to use the redshift dependence of the galaxy angular 2-point correlation function (2pCF)
to constrain cosmological parameters.
When an incorrect set of parameters is assumed for the coordinate transformation from redshift space to comoving space, 
it produces {\it redshift-dependent mis-scaling} in the constructed galaxy distribution.
As a result, we observe a redshift-dependent rescaling of the measured galaxy angular 2pCF.
Using mock galaxy catalogues (containing millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2) from the Horizon Run 4 N-body simulation, we find that the redshift evolution of the angular 2pCF shape, as a function of scale,
is sensitive to the adopted cosmological parameters. 
% mock galaxy catalogues having hundreds of millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2.
However, it is relatively insensitive to the gravitational growth of structure,
the galaxy bias, and the effect of redshift space distortions.
Analyzing the 2pCF shape on scales $5  h^{-1} {\rm Mpc} \leq r_\perp \leq 40 h^{-1} {\rm Mpc}$, 
we derive tight constraints on $\Omega_m$ and $w$ with 68.3\% CL uncertainties of 0.015 and 0.05.
%Our method is complementary to current works using 2pCF to constrain cosmological parameters.
The method could be applicable to future large scale structure surveys, especially photometric surveys such as DES, LSST, 
to derive tight cosmological constraints.
This work is a continuation of our previous works \citep{Li2014,Li2015,Li2016}
as a strategy to constrain cosmological parameters using redshift-invariant physical quantities;
they are all powerful in constrain cosmology and have a lot of merits,
e.g., are less affected by the systematic effects introduced by non-linear clustering or RSD,
does not require accurate modeling of galaxy clustering,
and are applicable on relative small clustering scales.
\end{abstract}

@@

The discovery of cosmic acceleration \citep{Riess1998,Perl1999} implies the existence of a ``dark energy'' component in the Universe 
or the breakdown of Einstein's gravity theory on cosmological scales.
The theoretical explanation and observational probe of cosmic acceleration has attracted 
tremendous effort in the last two decades and are still far from well understood or accurately measured \citep{SW1989,Li2011,DHW2013}.
%, but its properties still remain far from accurately known and its nature still remains mystery. 
%The simplest and currently favored solution is the additional field called dark energy which has negative pressure and is spatially homogeneous.
%The simplest explanation for dark energy is that it is a cosmological constant or vacuum energy, with constant equation of state (EoS) $w = -1$.

@@

Various statistical methods have been proposed to measure these effects.
The AP effect was first suggested to be measured through the anisotropic clustering of galaxies \citep{Ballinger1996,Matsubara1996}. Later, with the advent of large observational spectroscopic programs, this was applied to a series of LSS surveys
\citep{Outram2004,Blake2011,ChuangWang2012,Reid2012,Beutler2013,Linder2013,2014arXiv1407.2257S, Jeong2014,Sutter2014,2014ApJ...781...96L,Alam2016, Beutler2016, Sanchez2016}.
Although there have also been alternative approaches using the symmetry properties of galaxy pairs \citep{Marinoni2010,Jennings2011,BB2012}
and cosmic voids \citep{Ryden1995,LavausWandelt1995,Sutter2014,Qingqing2016}.
Methods proposed to measure the volume effect include the number counting of 
galaxy clusters \citep{PS1974,VL1996}, the topology of LSS \citep{topology},
the BAO scale \citep{EHT1998,BG03,SE03},
and the shape of 2pCF and power spectrum \citep{Sanchez2006,Sanchez2009}.

@@

\cite{Li2014} attempted to use the {\it galaxy density gradient field} 
to characterize the redshift evolution of the LSS distortion. 
We tested the idea on the Horizon Run 3 (HR3) N-body simulations \citep{horizonrun},
showing that the redshift evolution of the gradient field 
can be used to infer unbiased constraints on cosmological parameters and that it is, largely, insensitive to RSD.
The same topic was revisited in \cite{Li2015}, 
using a slightly modified version of the usual anisotropic galaxy two-point correlation function (2pCF), $\xi(\mu)$, 
where $\mu\equiv \cos \theta$ and $\theta$ is the angle between the connection of the galaxy pairs and the line of sight direction.
When an incorrect cosmological model is adopted, 
the shape of $\xi(\mu)$ is altered due to the anisotropic distortion of the LSS (the AP effect), 
and the amplitude is shifted due to the change in the comoving volume elements;
both effects have significant redshift dependence.
Although the RSD effect significantly distorts $\xi(\mu)$, 
it exhibits much less redshift evolution.
The method was applied to BOSS DR12 galaxies \citep{Li2016} to probe the redshift dependence of the AP effect, 
and we arrive at tight cosmological constraints competitive with mainstream probes of SNIa, BAO, CMB.

In this paper we continue our exploration of this strategy and present 
a new method using the redshift evolution of the shape of the {\it galaxy angular 2pCF} as a function of radial scale, $\omega(r_{\bot})$,
to constrain cosmology.
A wrongly adopted cosmology result in {\it redshift-dependent mis-scaling} of the galaxy distribution,
which leads to redshift-evolution of the shape of $\omega(r_{\bot})$.
The signal is sensitive to the cosmological parameters and relatively insensitive to the other effects such as the gravitational growth of structure,
the galaxy bias, and the RSD effect.
We apply our method to HR4 mock galaxies, using hundreds of millions of galaxies at redshifts $0\leq z\leq2$
and develop the statistical procedure to constrain cosmological parameters.

%In this paper we continue our series of work and probe to use the angular correlation function as a statistical tool to probing the volume effect in the angular direction.
%The method of redshift dependent AP effect has been shown great power to constrain cosmological parameters \cite{Li2014,Li2015,Li2015}.
%We hope this method also.
%The two methods probe different information encoded in the 2pCF and can be combined to fully probe the geometrical effect in LSS.
%Or one can also use the redshift evolution of 2D 2pCF xi(s,mu) to have all information included.
%We developed a method measuring the redshift of the shape of galaxy angular correlation function, $\hat \omega_{r_\perp}$, to constrain cosmology.
%A wrongly adopted cosmology result in redshift-dependent mis-scaling in the constructed galaxy distribution,
%which shifts apparent scale of the clustering patterns;
%this manifests itself as a redshift-dependent rescaling of the measured angular correlation function.
%We find this signal is sensitive to the adopted cosmological parameters and relatively insensitive to the gravitational growth of structure,
%the galaxy bias, and the RSD effect.
%We test our method on the HR4 mock galaxies.
%The method can be applied to current and future LSS surveys,
%especially, the photometric surveys such as DES and LSST which probe a large amount of galaxies and the large redshift error will not quite affect the angular 2pCF measurement.

@@

\begin{figure*}
   \centering{
   \includegraphics[height=8cm]{fig1_a.eps}
   \includegraphics[height=8.5cm]{fig1_b.eps}
   }
   \caption{\label{fig_xyquan}
   A description of how incorrectly assumed cosmologies can distort the interpretation of observation,
   assuming $\Omega_m=0.26,w=-1$ is the true cosmology. 
   Left panel shows a series of five regular squares, measured by an observer at the origin.
   Their true positions and shapes are plotted in blue dashed lines.
   When the observer adopts the wrong cosmologies to compute the distance from measured redshifts and infer the positions and shapes of the squares,
   he/she obtains distorted squares shown as the red solid lines.
   Right panel shows the redshift evolution of the wrongly estimated angular diameter distance (divided by the correct value).
   }
   % Need a better plot to show angular size variation!!!
\end{figure*}

@@

When incorrect values of $\Omega_m$ and $w$ are adopted, 
the inferred $\Delta r_{\parallel}$ and $\Delta r_{\perp}$ are also wrong,
resulting in wrong estimations of the object's shape (AP effect) and size (volume effect).
These effects and their cosmological consequences have been studied in \cite{Li2014,Li2015,Li2016}.

@@

An illustration is provided in the left panels of Figure \ref{fig_xyquan}.
Suppose that the true cosmology is a flat $\Lambda$CDM with present matter ratio $\Omega_m=0.26$
and standard dark energy EoS $w=-1$.
If we were to distribute a series of perfect squares at distances ranging from 500 Mpc/h to 3\,000 Mpc/h,
and an observer located at the origin were to measure their redshifts and infer the sizes of the squares
using the distance-redshift relations of four incorrect cosmologies
\begin{eqnarray}
 & &{\rm (i)}.\ \Omega_m=0.40,\ w=-1.0, \nonumber \\ 
 & &{\rm (ii)}.\ \Omega_m=0.15,\ w=-1.0, \nonumber\\ \noindent
 & &{\rm (iii)}.\ \Omega_m=0.26,\ w=-0.5,\nonumber\\ \noindent
 & &{\rm (iv)}.\ \Omega_m=0.26,\ w=-1.5,  \nonumber \noindent 
\end{eqnarray}
then the shapes of the squares appear distorted (AP effect),
and their sizes are wrongly estimated (volume effect).
Cosmological models (i,iii) result in compressed volume elements (in both angular and LOS direction),
and the degree of compression increases with increasing distance;
the situation is opposite for the other two cosmologies.

@@

In sum, as a consequence of incorrect cosmologies 
the size of objects is mis-estimated and the magnitude of mis-estimation depends on the redshift.
We use the galaxy angular 2pCF to probe the mis-estimation of angular size, ${\Delta r_{\perp, \rm wrong}}/{\Delta r_{\perp, \rm true}}$.

@@

The growth of structure increases the clustering and results in more compact structures,
while the volume effect maintains the clustering pattern and uniformly re-scales structures on all scales.
The imprint of each of these effects on the large scale structure is different and should be distinguishable.
In the following section we show that they affect the angular correlation function measurements in different ways, 
and thus can be easily separated.

@@

We use the angular 2pCF as a statistical tool to probe the volume effect.
The galaxy 2pCF as a function of galaxy separation in the angular direction, $\omega(r_\perp)$, is computed for snapshot data of mock galaxies at redshifts 0.5, 1, 1.5 and 2.
We adopt the Landy-Szalay estimator~\citep{1993ApJ...412...64L},
\begin{equation}
\omega(r_\perp)=\frac{DD-2DR+RR}{RR}\ ,
\end{equation}
where $DD$ is the number of galaxy--galaxy pairs, 
$DR$ the number of galaxy-random pairs, 
and $RR$ is the number of random--random pairs, 
all separated by a distance defined by $r_\perp\pm\Delta_{r_\perp}$ where we choose $\Delta_{r_\perp}=1h^{-1}\rm Mpc$.
The random catalogue consists of unclustered points uniformly distributed in the same space as the simulated data.. 
In an effort to reduce the statistical variance of the estimator, we use 50 times as many random points as we have galaxies.

@@

\subsection{Galaxy angular 2pCF: at different redshifts}\label{sec_2pCF_diffz}

\begin{figure*}
   \centering{
%   \includegraphics[width=18cm]{fig9_0.eps}
%   \includegraphics[width=18cm]{fig9_1.eps}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
    \includegraphics[width=18cm]{fig3.eps}
    \includegraphics[width=18cm]{fig3_b.eps}
   }
   \caption{\label{fig_diffz}
  The angular 2pCF ($\omega_{r_\perp}$, left panels), the shape of the angular 2pCF ($\hat{\omega}_{r_\perp}$, middle panels),
  and the evolution with respect to the $z=0$ value ($\hat{\omega}_{r_{\perp}}(z=z_i) - \hat{\omega}_{r_{\perp}}(z=0)$, right panels). 
  Upper panels show that in the correct cosmology the redshift evolution of the shape of 2pCF is rather small regardless of the large redshfit evolution of the amplitude, 
  whereas the lower panels show that, in a wrong cosmology $\Omega_m = 0.05,w=-1.5$, the redshift evolution of $\hat{\omega}_{r_\perp}$ is very significant.
   }
\end{figure*}

The upper-left panel of Figure \ref{fig_diffz} displays the angular 2pCF measured from HR4 mock galaxies. % (multiplied by scale $r$) in the five snapshot.
We multiply $\omega$ by the separation $r_\perp$ to have similar size of statistical uncertainty on all scales.
For convenience we will use the denotation
\begin{equation}
 \hat \omega_{r_{\perp}} \equiv r_{\perp} \omega.
\end{equation}

Among the different redshift bins there is large variation in the amplitude of $\omega(r_\perp)$.
The amplitude is proportional to the clustering strength, which is affected by the gravitational growth of structures and the galaxy bias.
The amplitude is highest at $z=0$ where the structures experienced the most growth.
$\omega(r_\perp)$ increases at $z>1$ with increasing redshift 
as a reason of increasing galaxy bias.
%leading to stronger clustering strength and higher amplitude of 2pCF.
%On the contrary, at higher redshift we find $\omega(z=2)>\omega(z=1.5)>\omega(z=1)$,
%The trend is different from $z=1,1.5,2$,
%simply because by applying a uniform mass cut we are selecting more biased galaxies at higher redshift.

Although there is large variation in amplitude between the different redshifts bins, 
%The shape of $r_\perp\omega$ also evolves with redshift.
the shape of $\omega_{r_{\perp}}$  remains similar at all redshifts;
in general it peaks at $r\sim9 h^{-1}\rm Mpc$ and monotonically drops or increases at larger or smaller scales.
The only exception is the small enhancement at $r\lesssim 2 h^{-1}\rm Mpc$,
which is caused by the non-linear growth of structures 
and is much more significant at lower redshift.

In order to directly compare the shape of the 2pCF at different redshifts,
in the middle panel of Figure \ref{fig_diffz} 
we show the $r_\perp\omega$ normalized by the overall amplitude within 
$5h^{-1}{\rm Mpc} < r < 40h^{-1}{\rm Mpc}$
(here after $\hat \omega_{r_\perp}$):
\begin{equation}
 \hat \omega_{ r_\perp} \equiv  \frac{ {r_\perp\omega}(r_{\perp})}{ \int_{r_{\perp, \rm min}}^{r_{\perp, \rm max}}r_{\perp} \omega(r_{\perp}) d r_{\perp} / (r_{\perp,\rm max}-r_{\perp,\rm min}) },
\end{equation}
where we choose $r_{\perp, \rm min}=5 h^{-1}$ Mpc, $r_{\perp, \rm max}=40 h^{-1}$ Mpc in this analysis.
Below $5 h^{-1}$ Mpc the non-linear growth of structure 
leads to systematic redshift evolution which could be difficult to be reliably accounted;
On scales larger than $40 h^{-1}$ Mpc,
the analytical modeling of the shape of the angular 2pCF is relatively well understood;
one can just fit the 2pCF with the theoretical predictions \citep{BCGS2001,Salvador2014,Salvador2016} 
instead of using our method 
(although our method should also be applicable).

In the upper-middle panel, the overlapping of $\hat\omega_{r_{\perp}}$
clearly show the minimal redshift evolution of the shape.
In the upper-right panel, 
we further show the residual evolution at high redshifts 
with respect to $z=0$.
There is only 1-4\% enhancement 
at $r<10h^{-1}\rm Mpc$,
and $<1.5\%$ suppression at $r>25 h^{-1}\rm Mpc$.
The trend is monotonic with redshift.

>>>>

\title{Cosmological constraints from the redshift dependence of the volume effect using the galaxy 2-point correlation function across the line-of-sight}

%\author{Xiao-Dong~Li\altaffilmark{1}, Changbom~Park\altaffilmark{1}, J.~E.~Forero-Romero\altaffilmangulatark{2} and Juhan Kim%\altaffilmark{3}}
%\affil{\altaffilmark{1}School of Physics, Korea Institute for Advanced Study, Heogiro 85, Seoul 130-722, Korea }
%\affil{\altaffilmark{2}Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, %Colombia}
%\affil{\altaffilmark{3}Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-%gu, Seoul 130-722, Korea }
%\affil{\it (xiaodongli@kias.re.kr, cbp@kias.re.kr, je.forero@uniandes.edu.co, kjhan@kias.re.kr)}

@@

\author{Xiao-Dong Li, Changbom Park, }
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\author{Cristiano G. Sabiu\altaffilmark{1}, Hyunbae Park, }
\affil{Korea Astronomy and Space Science Institute, Daejeon 305-348, Korea}
%\author{David H. Weinberg,}
%\affil{Department of Astronomy and CCAPP, The Ohio State University, 140 West 18th Avenue, Columbus, OH 43210, USA}
%\author{Donald P. Schneider,}
%\affil{Department of Astronomy and Astrophysics, The Pennsylvania State University, 
%University Park, PA 16802 }
%\affil{Institute for Gravitation and the Cosmos, The Pennsylvania State University, 
%University Park, PA 16802 }
\author{Cheng Cheng, }
\affil{Kavli Institute for Theoretical Physics China, Institute of Theoretical Physics, Chinese Academy of Sciences, Zhong Guan Cun Street 55\#, Beijing, 100190, P.R. China}
\affil{University of Chinese Academy of Sciences, P.R. China}
\author{Juhan Kim,}
\affil{Center for Advanced Computation, Korea Institute for Advanced Study, 85 Hoegi-ro, Dongdaemun-gu, Seoul 130-722, Korea}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\and
\author{Sungwook E. Hong}
\affil{School of Physics, Korea Institute for Advanced Study, 85 Heogiro, Dongdaemun-gu, Seoul 130-722, Korea}
\affil{Korea Astronomy and Space Science Institute, Daejeon 305-348, Korea}

@@

\begin{abstract}
We propose to use the redshift dependence of the galaxy 2-point correlation function across the line-of-sight (2pCF), $\xi(r_{\bot})$, to constrain cosmological parameters.
When an incorrect set of parameters is assumed for the coordinate transformation from redshift space to comoving space, 
it produces {\it redshift-dependent mis-scaling} in the constructed galaxy distribution.
As a result, we observe a redshift-dependent rescaling of the measured $\xi(r_{\bot})$.
Using mock galaxy catalogues (containing millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2) from the Horizon Run 4 N-body simulation, we find that the redshift evolution of the $\xi(r_{\bot})$ shape, as a function of scale,
is sensitive to the adopted cosmological parameters. 
% mock galaxy catalogues having hundreds of millions of galaxies at redshifts 0, 0.5, 1, 1.5, 2.
However, it is relatively insensitive to the gravitational growth of structure,
the galaxy bias, and the effect of redshift space distortions.
Analyzing the 2pCF shape on scales $5  h^{-1} {\rm Mpc} \leq r_\perp \leq 40 h^{-1} {\rm Mpc}$, 
we derive tight constraints on $\Omega_m$ and $w$ with 68.3\% CL uncertainties of 0.015 and 0.05.
%Our method is complementary to current works using 2pCF to constrain cosmological parameters.
The method could be applicable to future large scale structure surveys, especially photometric surveys such as DES, LSST, 
to derive tight cosmological constraints.
This work is a continuation of our previous works \citep{Li2014,Li2015,Li2016}
as a strategy to constrain cosmological parameters using redshift-invariant physical quantities;
they are all powerful in constrain cosmology and have a lot of merits,
e.g., are less affected by the systematic effects introduced by non-linear clustering or RSD,
does not require accurate modeling of galaxy clustering,
and are applicable on relative small clustering scales.
\end{abstract}

@@

The discovery of cosmic acceleration \citep{Riess1998,Perl1999} implies the existence of a ``dark energy'' component in the Universe 
or the breakdown of Einstein's gravity theory on cosmological scales \citep[see ][for a recent review]{2012IJMPD..2130002Y}.
The theoretical explanation and observational probe of cosmic acceleration has attracted 
tremendous effort in the last two decades and are still far from well understood or accurately measured \citep{SW1989,Li2011,DHW2013}.
%, but its properties still remain far from accurately known and its nature still remains mystery. 
%The simplest and currently favored solution is the additional field called dark energy which has negative pressure and is spatially homogeneous.
%The simplest explanation for dark energy is that it is a cosmological constant or vacuum energy, with constant equation of state (EoS) $w = -1$.

@@

Various statistical methods have been proposed to measure these effects.
The AP effect was first suggested to be measured through the anisotropic clustering of galaxies \citep{Ballinger1996,Matsubara1996}. Later, with the advent of large observational spectroscopic programs, this was applied to a series of LSS surveys
\citep{Outram2004,Blake2011,ChuangWang2012,Reid2012,Beutler2013,Linder2013,2014arXiv1407.2257S, Jeong2014,Sutter2014,2014ApJ...781...96L,Alam2016, Beutler2016, Sanchez2016}, while considering the detailed effect of systematics for unbiased estimates of $D_A(z)$ and $H(z)$ \citep{2014MNRAS.445....2V,2016MNRAS.tmp.1473R,2016arXiv160302389S}.

Although there have also been alternative approaches using the symmetry properties of galaxy pairs \citep{Marinoni2010,Jennings2011,BB2012}
and cosmic voids \citep{Ryden1995,LavausWandelt1995,Sutter2014,Qingqing2016}.
Methods proposed to measure the volume effect include the number counting of 
galaxy clusters \citep{PS1974,VL1996}, the topology of LSS \citep{topology},
the BAO scale \citep{EHT1998,BG03,SE03},
and the shape of 2pCF and power spectrum \citep{Sanchez2006,Sanchez2009}.

@@

\cite{Li2014} attempted to use the {\it galaxy density gradient field} 
to characterize the redshift evolution of the LSS distortion. 
We tested the idea on the Horizon Run 3 (HR3) N-body simulations \citep{horizonrun},
showing that the redshift evolution of the gradient field 
can be used to infer unbiased constraints on cosmological parameters and that it is, largely, insensitive to RSD.
The same topic was revisited in \cite{Li2015}, 
using a slightly modified version of the usual anisotropic galaxy two-point correlation function (2pCF), $\xi(\mu)$, 
where $\mu\equiv \cos \theta$ and $\theta$ is the angle between the connection of the galaxy pairs and the line of sight direction.
When an incorrect cosmological model is adopted, 
the shape of $\xi(\mu)$ is altered due to the anisotropic distortion of the LSS (the AP effect), 
and the amplitude is shifted due to the change in the comoving volume elements;
both effects have significant redshift dependence.
Although the RSD effect significantly distorts $\xi(\mu)$, 
it exhibits much less redshift evolution.
The method was applied to BOSS DR12 galaxies \citep{Li2016} to probe the redshift dependence of the AP effect, 
and we arrive at tight cosmological constraints competitive with the mainstream probes of SNIa, BAO, and CMB.

In this paper we continue our exploration of this strategy and present 
a new method using the redshift evolution of the shape of the 2-point correlation function across the line-of-sight as a function of radial scale, $\xi(r_{\bot})$,
to constrain cosmology.
A wrongly adopted cosmology results in {\it redshift-dependent mis-scaling} of the galaxy distribution,
which leads to redshift-evolution of the shape of $\xi(r_{\bot})$.
The signal is sensitive to the cosmological parameters but relatively insensitive to the other effects such as the gravitational growth of structure,
the galaxy bias, and the RSD effect.
We apply our method to HR4 mock catalogues, using hundreds of millions of galaxies at redshifts $0\leq z\leq2$
and develop the statistical procedure to constrain cosmological parameters.

%In this paper we continue our series of work and probe to use the angular correlation function as a statistical tool to probing the volume effect in the angular direction.
%The method of redshift dependent AP effect has been shown great power to constrain cosmological parameters \cite{Li2014,Li2015,Li2015}.
%We hope this method also.
%The two methods probe different information encoded in the 2pCF and can be combined to fully probe the geometrical effect in LSS.
%Or one can also use the redshift evolution of 2D 2pCF xi(s,mu) to have all information included.
%We developed a method measuring the redshift of the shape of galaxy angular correlation function, $\hat \xi_{r_\perp}$, to constrain cosmology.
%A wrongly adopted cosmology result in redshift-dependent mis-scaling in the constructed galaxy distribution,
%which shifts apparent scale of the clustering patterns;
%this manifests itself as a redshift-dependent rescaling of the measured angular correlation function.
%We find this signal is sensitive to the adopted cosmological parameters and relatively insensitive to the gravitational growth of structure,
%the galaxy bias, and the RSD effect.
%We test our method on the HR4 mock galaxies.
%The method can be applied to current and future LSS surveys,
%especially, the photometric surveys such as DES and LSST which probe a large amount of galaxies and the large redshift error will not quite affect the angular 2pCF measurement.

@@

\begin{figure*}
   \centering{
   \includegraphics[height=8cm]{fig1_a.eps}
   \includegraphics[height=8.5cm]{fig1_b.eps}
   }
   \caption{\label{fig_xyquan}
   A description of how incorrectly assumed cosmologies can distort the interpretation of observation,
   assuming $\Omega_m=0.26,w=-1$ is the true cosmology. 
   Left panel shows a series of five regular squares, measured by an observer at the origin.
   Their true positions and shapes are plotted in blue dashed lines.
   When the observer adopts incorrect cosmologies when computing distances from redshifts and infering the positions and shapes of the squares,
   they obtain distorted shapes (red solid lines).
   Right panel shows the redshift evolution of the wrongly estimated angular diameter distance (divided by the correct value).
   }
   % Need a better plot to show angular size variation!!!
\end{figure*}

@@

When incorrect values of $\Omega_m$ and $w$ are adopted, 
the inferred $\Delta r_{\parallel}$ and $\Delta r_{\perp}$ are also incorrect,
resulting in erroneous estimation of the object's shape (AP effect) and size (volume effect).
These effects and their cosmological consequences have been studied in \cite{Li2014,Li2015,Li2016}.

@@

An illustration is provided in the left panels of Figure \ref{fig_xyquan}.
Suppose that the true cosmology is a flat $\Lambda$CDM with present matter ratio $\Omega_m=0.26$
and standard dark energy EoS $w=-1$.
If we were to distribute a series of perfect squares at distances ranging from 500 Mpc/h to 3\,000 Mpc/h,
and an observer located at the origin were to measure their redshifts and infer the sizes of the squares
using the distance-redshift relations of four incorrect cosmologies
\begin{eqnarray}
 & &{\rm (i)}.\ \Omega_m=0.40,\ w=-1.0, \nonumber \\ 
 & &{\rm (ii)}.\ \Omega_m=0.15,\ w=-1.0, \nonumber\\ \noindent
 & &{\rm (iii)}.\ \Omega_m=0.26,\ w=-0.5,\nonumber\\ \noindent
 & &{\rm (iv)}.\ \Omega_m=0.26,\ w=-1.5,  \nonumber \noindent 
\end{eqnarray}
then the shapes of the squares would appear distorted (AP effect),
and their sizes would be wrongly estimated (volume effect).
Cosmological models (i,iii) result in compressed volume elements (in both angular and LOS directions),
and the degree of compression increases with increasing distance;
the situation is opposite for the other two cosmologies.

@@

In sum, as a consequence of incorrect cosmologies 
the size of objects is mis-estimated and the magnitude of mis-estimation depends on the redshift.
We use the galaxy 2pCF across the line-of-sight to probe the mis-estimation of angular size, ${\Delta r_{\perp, \rm wrong}}/{\Delta r_{\perp, \rm true}}$.

@@

The growth of structure increases the clustering and results in more compact structures,
while the volume effect maintains the clustering pattern and uniformly re-scales structures on all scales.
The imprint of each of these effects on the large scale structure is different and should be distinguishable.
In the following section we show that they affect $\xi(r_{\bot})$ measurements in different ways, 
and thus can be easily separated.

@@

We use the 2pCF across the line-of-sight as a statistical tool to probe the volume effect.
The galaxy 2pCF as a function of galaxy separation perpendicular to the LOS, $\xi(r_\perp)$, is computed for snapshot data of mock galaxies at redshifts 0.5, 1, 1.5 and 2.
We adopt the Landy-Szalay estimator~\citep{1993ApJ...412...64L},
\begin{equation}
\xi(r_\perp)=\frac{DD-2DR+RR}{RR}\ ,
\end{equation}
where $DD$ is the number of galaxy--galaxy pairs, 
$DR$ the number of galaxy-random pairs, 
and $RR$ is the number of random--random pairs, 
all separated by a distance defined by $r_\perp\pm\Delta_{r_\perp}$ where we choose $\Delta_{r_\perp}=1h^{-1}\rm Mpc$.
The random catalogue consists of unclustered points uniformly distributed in the same space as the simulated data. 
In an effort to reduce the statistical variance of the estimator, we use 50 times as many random points as we have galaxies.

@@

\subsection{Galaxy 2pCF across the line-of-sight: at different redshifts}\label{sec_2pCF_diffz}

\begin{figure*}
   \centering{
%   \includegraphics[width=18cm]{fig9_0.eps}
%   \includegraphics[width=18cm]{fig9_1.eps}
%   \includegraphics[height=8cm]{Tpcf--plot--Normed.eps}
%    \includegraphics[height=8cm]{smu.eps}
 %   \includegraphics[width=18cm]{fig3.eps}
%    \includegraphics[width=18cm]{fig3_b.eps}
    \includegraphics[width=2\columnwidth]{fig3.eps}
    \includegraphics[width=2\columnwidth]{fig3_b.eps}
   }
   \caption{\label{fig_diffz}
  The 2pCF across the line-of-sight, $\xi_{r_\perp}$ (left panels), the shape of $\hat{\xi}_{r_\perp}$ (middle panels),
  and the evolution with respect to the $z=0$ value, $\hat{\xi}_{r_{\perp}}(z=z_i) - \hat{\xi}_{r_{\perp}}(z=0)$ (right panels). 
  Upper panels show that in the correct cosmology the redshift evolution of the shape of 2pCF is rather small regardless of the large redshfit evolution of the amplitude, 
  whereas the lower panels show that, in a wrong cosmology $\Omega_m = 0.05,w=-1.5$, the redshift evolution of $\hat{\xi}_{r_\perp}$ is very significant.
   }
\end{figure*}

The upper-left panel of Figure \ref{fig_diffz} displays the 2pCF across the line-of-sight measured from HR4 mock galaxies. % (multiplied by scale $r$) in the five snapshot.
We multiply $\xi$ by the separation $r_\perp$ to obtain a similar statistical uncertainty on all scales.
For convenience we will use the denotation
\begin{equation}
 \hat \xi_{r_{\perp}} \equiv r_{\perp} \xi.
\end{equation}

Among the different redshift bins there is large variation in the amplitude of $\xi(r_\perp)$.
The amplitude is proportional to the clustering strength, which is affected by the gravitational growth of structures and the galaxy bias.
The amplitude is highest at $z=0$ where the structures experienced the most growth.
$\xi(r_\perp)$ increases at $z>1$ with increasing redshift 
due to the increasing galaxy bias.
%leading to stronger clustering strength and higher amplitude of 2pCF.
%On the contrary, at higher redshift we find $\xi(z=2)>\xi(z=1.5)>\xi(z=1)$,
%The trend is different from $z=1,1.5,2$,
%simply because by applying a uniform mass cut we are selecting more biased galaxies at higher redshift.

Although there is large variation in amplitude between the different redshifts bins, 
%The shape of $r_\perp\xi$ also evolves with redshift.
the shape of $\xi_{r_{\perp}}$  remains similar at all redshifts;
in general it peaks at $r\sim9 h^{-1}\rm Mpc$ and monotonically drops or increases at larger or smaller scales.
The only exception is the small enhancement at $r\lesssim 2 h^{-1}\rm Mpc$,
which is caused by the non-linear growth of structures 
and is much more significant at lower redshift.

In order to directly compare the shape of the 2pCF at different redshifts,
in the middle panel of Figure \ref{fig_diffz} 
we show the $r_\perp\xi$ normalized by the overall amplitude within 
$5h^{-1}{\rm Mpc} < r < 40h^{-1}{\rm Mpc}$
(here after $\hat \xi_{r_\perp}$):
\begin{equation}
 \hat \xi_{ r_\perp} \equiv  \frac{ {r_\perp\xi}(r_{\perp})}{ \int_{r_{\perp, \rm min}}^{r_{\perp, \rm max}}r_{\perp} \xi(r_{\perp}) d r_{\perp} / (r_{\perp,\rm max}-r_{\perp,\rm min}) },
\end{equation}
where we choose $r_{\perp, \rm min}=5 h^{-1}$ Mpc, $r_{\perp, \rm max}=40 h^{-1}$ Mpc in this analysis.
Below $5 h^{-1}$ Mpc the non-linear growth of structure 
leads to systematic redshift evolution which could be difficult to be reliably accounted;
On scales larger than $40 h^{-1}$ Mpc,
the analytical modeling of the shape of $\xi_{r_{\perp}}$ is relatively well understood;
one can just fit the 2pCF with the theoretical predictions \citep{BCGS2001,Salvador2014,Salvador2016} 
instead of using our method 
(although our method should also be applicable).

In the upper-middle panel, the overlapping of $\hat\xi_{r_{\perp}}$
clearly show the minimal redshift evolution of the shape.
In the upper-right panel, 
we further show the residual evolution at high redshifts 
with respect to $z=0$.
There is only 1-4\% enhancement 
at $r<10h^{-1}\rm Mpc$,
and $<1.5\%$ suppression at $r>25 h^{-1}\rm Mpc$.
The trend is monotonic with redshift.
